% Source: https://github.com/sb2nov/resume

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nguyen Huy Thanh}} & Email: \href{mailto:thanhnguyen2187@gmail.com}{thanhnguyen2187@gmail.com}\\
  \href{https://nguyenhuythanh.com/resume.pdf}{https://nguyenhuythanh.com/resume.pdf} & Mobile: +84-392-325-966 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Wombat Exchange}{Software Engineer}
      {Remote, Hongkong SAR}{7/2023 -- Now}
      \resumeItemListStart
        \resumeItem{EVM Data Indexing}
          {Maintained and deployed subgraphs for 3+ EVM chains, which handled
          more than 300,000 events. The subgraphs served Wombat Analytics
          page, which has nearly 250,000 monthly requests. Optimized Wombat
          Analytics page's loading time from 10+ seconds to 1 second.

          Technologies used: Subgraph, AssemblyScript, TypeScript, NextJS,
          Vercel.}
      \resumeItemListEnd

    \resumeSubheading
      {Xantus}{Software Engineer}
      {Le Van Luong, Thanh Xuan, Hanoi}{10/2021 -- 12/2022}
      \resumeItemListStart
        \resumeItem{EVM Data Indexing}
          {Designed, implemented, deployed, and optimized Events Synchronization
          services for 10+ EVM-compatible Smart Contracts on 3+ chains. The
          services provide on-chain data for 3+ projects (Mones, Gunfire Avax,
          and Oxalus NFT Aggregator).

          Technologies used: Apache Kafka, TypeScript, web3js, Golang,
          go-ethereum.}
      \resumeItemListEnd

    \resumeSubheading
      {Teko Vietnam}{Software Engineer, Data Platform Engineer}
      {Hoang Cau, Dong Da, Hanoi}{4/2021 -- 1/2022}
      \resumeItemListStart
        \resumeItem{Master Product Data}
          {Designed, implemented, and deployed data pipelines, data models, and
          REST API of Product Matching service for 10k+ products.

          Technologies used: Python, Golang, FastAPI, underthesea.}
        \resumeItem{Real-time Analytics Storage Layer}
          {Tested, deployed, and operated Apache Druid as the storage layer for
          real-time analytics for 1m+ events.

          Technologies used: Google Cloud, Kubernetes, Docker, Apache Druid,
          Apache Kafka, GitLab CI.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Viettel Cyber Security}{Software Engineer, System Engineer}
    %   {Me Tri, Tu Liem, Hanoi}{9/2020 -- 1/2021}
    %   \resumeItemListStart
    %     \resumeItem{Network Visualization}
    %       {Designed, implemented, and deployed Network Visualization module for
    %       the company's internal project.
    %
    %       Technologies used: Python, JavaScript, Flask, GoJS.}
    %   \resumeItemListEnd

    \resumeSubheading
      {AI Academy Vietnam}{Software Engineer, System Engineer}
      {Hoang Quoc Viet, Nghia Tan, Hanoi}{6/2019 -- 8/2020}
      \resumeItemListStart
        \resumeItem{Scheduled News Aggregation}
          {Designed, implemented, and deployed Data Aggregating (crawling) for
          50+ news sources.

          Technologies used: Python, RabbitMQ, APScheduler, pika.}
        \resumeItem{Time Series Prediction}
          {Designed, implemented, and deployed configurable Prediction service
          that can use 10+ prediction models.

          Technologies used: Python, sklearn, statsmodels.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education \& Certification}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Le Quy Don Technical University}{Engineer, Software Engineering}
      {Hoang Quoc Viet, Nghia Tan, Hanoi}{6/2016 -- 6/2021}
      \resumeItemListStart
        \resumeItem{GPA} {3.13}
        \resumeItem{Specialized Individuals Informatics Olympiad 2017} {Second Prize}
        \resumeItem{Super Cup Informatics Olympiad 2018} {Third Prize}
      \resumeItemListEnd
    \resumeSubheading
      {IELTS issued by British Council}{Academic Module}
      {Tay Ho, Hanoi}{2/2023}
      \resumeItemListStart
        \resumeItem{Overall} {7.5}
        \resumeItem{TRF Number} {22VN027313NGUH002A}
        % \resumeItem{Made the teacher my girlfriend} {By some miracles and a lot of hardships}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------SIDE PROJECTS-----------
\section{Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Crypta}
      {An offline-first code snippet manager. Deployed at: 
      \href{https://thanhnguyen2187.github.io/crypta}{https://thanhnguyen2187.github.io/crypta}.}
    \resumeSubItem{Darkest Savior}
      {A low-level Golang library and CLI tool to convert Darkest Dungeon's
      proprietary save format to JSON and vice versa. Source at:
      \href{https://github.com/thanhnguyen2187/darkest-savior}{https://github.com/thanhnguyen2187/darkest-savior}.}
    \resumeSubItem{CamLisp}
      {A simple Lisp/Scheme interpreter in OCaml. Source at:
      \href{https://github.com/thanhnguyen2187/camlisp}{https://github.com/thanhnguyen2187/camlisp}.}
  \resumeSubHeadingListEnd

%--------SKILLS AND INTERESTS-----------
\section{Skills \& Interests}
  \resumeSubHeadingListStart
    \resumeSubItem{Skills}{Python; JavaScript/TypeScript; Golang; Vim; tmux.}
    \resumeSubItem{Interests}{fantasy novels; challenging videogames; playing
    the guitar and singing along.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
